Deep Reinforcement Learning for Conservation Decisions

### 2022-06-01 manuscript/revision_response.Rmd
Adding training details in results
Making sure line nos are correct

All algorithms were run on an NVIDIA Quadro RTX 8000 GPU. The training  budget for the fishing scenario was 300K timesteps (3K runs, taking about 25 minutes). Tipping point training budget was 3M timesteps (6K runs, taking around 3 hours). Precise run times vary with machine load and algorithm. Software details and hyperparameters are provided in the associated GitHub repo, https://github.com/boettiger-lab/rl-intro/. Hyperparameter tuning typically required 100s of training runs using both Optuna and manual adjustments.

@@

Regarding how neural networks can be used, we have attempted to clarify this in the manuscript:

@@

We’ve updated this statement as we have found a few note-worthy applications in ecology. Cite !!line!!.

@@

We agree the writing was not clear, we have sought to simplify this in the intro, sticking with Levins 1966 famous characterization. The essence of Levins' classic argument is merely that process-based models with only a handful of parameters are often more general than those with scores of parameters. We return to this point, though not this language, in the Discussion addressing how real-world simulations will be more complex then the benchmarks we have chosen for this intro. We avoid the language of tactical (i.e. 'use this precise policy or algorithm on this precise problem') vs strategic (i.e. ;evaluate the use RL as a strategy in conservation problems') as relatively unhelpful here.

@@

The difficulty around evaluating and interpreting ML models will be a significant obstacle to RL’s adoption on safety-critical problems. For large observation-action spaces, there are no general tools that will let you interpret the model, so practitioners must carry out extensive testing to gain confidence in the agent; but, extensive testing for large (aka non-tabular) observation-action spaces will not guarantee that the agent won’t commit undesirable actions on untested situations. We provided a small update to address these points which are open research questions:

“Since deep neural networks lack transparency [@castelvecchi_can_2016], can we be confident that the agent will generalize its past experience to new situations -- especially when we cannot readily visualize the policy?”

@@

We have updated our description of the discount factor in the manuscript to address these questions:

@@

This is a great question that we have tried to address in the latest revision,

@@

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. This is something that we alluded to in line xxx,

@@

The reviewer raises two important issues here: "What is the appropriate reward function", and "What are the appropriate limitations on the action space". These questions have always been central issues to ecological management and decision-making, and are neither unique to or resolved by the use RL [@gregory_structured_2012; @conroy_decision_2013]. We have changed some of the language in “RL Environments” to better address the action space question:

@@

And we address the difficulty in selecting a reward function in the discussion:

@@

Lines 216-218: “The manager seeks to optimize the net present value (discounted cumulative catch) of a fishery, observing the stock size each year and setting an appropriate harvest quota in response.”

And for the tipping point problem we give a full detailed explanation of the problem from lines 265 to 280.

@@

We share this perspective with the reviewer that our study does not prove that deep RL can be immediately applied to conservation problems. Validating RL as method for ecological problems is not the intention of our paper. Instead, we have written our paper to be an introduction for ecologists to deep RL, whereby we introduce the OpenAI Gym framework, some fundamental RL concepts and example problems, so that researchers can investigate deep RL on their own and better understand how it is beginning to be applied to ecology. We are at a point in time where researchers and organizations are using deep RL in conservation contexts, so it is imperative for our community to start understanding the benefits and downfalls of using deep RL for our specialized class of problems.

!!edit intro to to voice this intention CC Carl!!

@@

We have added a discussion of scaling in the appendix.

>>>>

All algorithms were run on an NVIDIA Quadro RTX 8000 GPU. The training  budget for the fishing scenario was 300K timesteps (3K runs, taking about 25 minutes). Tipping point training budget was 3M timesteps (6K runs, taking around 3 hours). Precise run times vary with machine load and algorithm. Software details and hyperparameters are provided in the associated GitHub repo, https://github.com/boettiger-lab/rl-intro/. Hyperparameter tuning typically required 100s of training runs using both Optuna and manual adjustments. We have added these details to the manuscript in lines 199-206.

@@

Regarding how neural networks can be used, we have attempted to clarify this in the manuscript in lines 150-153:

@@

We’ve updated this statement in the introduction (lines 42-43) as we have found a few note-worthy applications in ecology from @xu_robust_2021 and @silvestro_improving_2022.

@@

We agree the writing was not clear, we have sought to simplify this in the intro, sticking with Levins 1966 famous characterization. The essence of Levins' classic argument is merely that process-based models with only a handful of parameters are often more general than those with scores of parameters. We return to this point, though not this language, in the Discussion addressing how real-world simulations will be more complex then the benchmarks we have chosen for this intro. We avoid the language of tactical (i.e. 'use this precise policy or algorithm on this precise problem') vs strategic (i.e. ;evaluate the use RL as a strategy in conservation problems') as relatively unhelpful here. We updated lines 79-84 as follows:

@@

The difficulty around evaluating and interpreting ML models will be a significant obstacle to RL’s adoption on safety-critical problems. For large observation-action spaces, there are no general tools that will let you interpret the model, so practitioners must carry out extensive testing to gain confidence in the agent; but, extensive testing for large (aka non-tabular) observation-action spaces will not guarantee that the agent won’t commit undesirable actions on untested situations. We provided a small update to address these points in lines 395-399:

“Since deep neural networks lack transparency [@castelvecchi_can_2016], can we be confident that the agent will generalize its past experience to new situations -- especially when we cannot readily visualize the policy? To gain such confidence, it will be necessary to do extensive testing on previously unseen contexts, but even then, it can be difficult to verify that the agent will perform as expected.”

@@

We have updated our description of the discount factor in the manuscript to address these questions in lines 186-187:

@@

This is a great question that we have tried to address in the latest revision in lines 244-250:

@@

The reviewer here raises a very good point here about employing domain knowledge to reduce computational costs. This is something that we alluded to in lines 409-411:

@@

The reviewer raises two important issues here: "What is the appropriate reward function", and "What are the appropriate limitations on the action space". These questions have always been central issues to ecological management and decision-making, and are neither unique to or resolved by RL [@gregory_structured_2012; @conroy_decision_2013]. We have changed some of our language in lines 126-128 to better address the action space question:

@@

And we address the difficulty in selecting a reward function in the discussion in lines 399-401:

@@

Lines 221-223: “The manager seeks to optimize the net present value (discounted cumulative catch) of a fishery, observing the stock size each year and setting an appropriate harvest quota in response.”

And for the tipping point problem we give a full detailed explanation of the problem from lines 269 to 285.

@@

We share this perspective with the reviewer that our study does not prove that deep RL can be immediately applied to conservation problems. Validating RL as method for ecological problems is not the intention of our paper. Instead, we have written our paper to be an introduction for ecologists to deep RL, whereby we introduce the OpenAI Gym framework, some fundamental RL concepts and example problems, so that researchers can investigate deep RL on their own and better understand how it is beginning to be applied to ecology. We are at a point in time where researchers and organizations are using deep RL in conservation contexts, so it is imperative for our community to start understanding the benefits and downfalls of using deep RL for our specialized class of problems. We have edited the introduction in lines 99-105 to address this comment.

@@

We have added a discussion of scaling in Appendix C.
